\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Simple Machines Problem Series}
\author{Michael Xie, \\ Jack Miner Public School, \\ Grade 8, Professor Gibson}
\date{\today}

\begin{document}

\maketitle

\section*{Problem set (1)}

\begin{enumerate}
    \item What would the mechanical advantage be of a lever system that can lift 100N with an effort force of only 25N? Use the GRASS method for your calculations.
    \item What would the maximum load that a lever could lift if its mechanical advantage is 3 and the effort force applied to the lever is 30N? Use the GRASS method for your calculations.
    \item What effort force would be needed to lift a load of 150N with a lever system that has a mechanical advantage of 3.5? Use the GRASS method for your calculations.
    \item What is the DE of an inclined plane that is 2 m high and has a mechanical advantage of 0.5? Use GRASS method.
\end{enumerate}

\subsection*{Solutions for Problem set (1)}

\begin{enumerate}
    \item \textbf{Given:} Load $= 100\,\mathrm{N}$, Effort $= 25\,\mathrm{N}$ \\
    \textbf{Required:} Mechanical Advantage (MA) \\
    \textbf{Analysis:}
    \[
        \mathrm{MA} = \frac{\text{Load}}{\text{Effort}}
    \]
    \textbf{Solution:}
    \[
        \mathrm{MA} = \frac{100\,\mathrm{N}}{25\,\mathrm{N}} = 4
    \]
    \textbf{Statement:} The mechanical advantage is $4$.

    \item \textbf{Given:} $\mathrm{MA} = 3$, Effort $= 30\,\mathrm{N}$ \\
    \textbf{Required:} Maximum Load \\
    \textbf{Analysis:}
    \[
        \text{Load} = \mathrm{MA} \times \text{Effort}
    \]
    \textbf{Solution:}
    \[
        \text{Load} = 3 \times 30\,\mathrm{N} = 90\,\mathrm{N}
    \]
    \textbf{Statement:} The maximum load is $90\,\mathrm{N}$.

    \item \textbf{Given:} Load $= 150\,\mathrm{N}$, $\mathrm{MA} = 3.5$ \\
    \textbf{Required:} Effort \\
    \textbf{Analysis:}
    \[
        \text{Effort} = \frac{\text{Load}}{\mathrm{MA}}
    \]
    \textbf{Solution:}
    \[
        \text{Effort} = \frac{150\,\mathrm{N}}{3.5} \approx 42.86\,\mathrm{N}
    \]
    \textbf{Statement:} The effort force needed is approximately $42.86\,\mathrm{N}$.

    \item \textbf{Given:} Height $= 2\,\mathrm{m}$, $\mathrm{MA} = 0.5$ \\
    \textbf{Required:} DE (Distance Effort) \\
    \textbf{Analysis:}
    \[
        \mathrm{MA} = \frac{\mathrm{DE}}{\mathrm{DR}}, \quad \mathrm{DE} = \mathrm{MA} \times \mathrm{DR}
    \]
    \textbf{Solution:}
    \[
        \mathrm{DE} = 0.5 \times 2\,\mathrm{m} = 1\,\mathrm{m}
    \]
    \textbf{Statement:} The DE is $1$ meter.
\end{enumerate}

\section*{Problem set (2)}

\begin{enumerate}
    \item I push with 400 N on a couch. The couch moves 2 m. How much work am I doing?
    \item Mr. Oliver moved his desk 2m. He did 150J of work. How much force did he exert?
    \item Mrs. Hutchinson exerted 20 N of force to move a rock in her garden. She did 400 J of work. How far did she move the rock?
    \item Ms Tilden is exerting 400 N of force on her door, but it won't open. How much work did she do?
\end{enumerate}

\subsection*{Solutions for Problem set (2)}

\begin{enumerate}
    \item \textbf{Given:} Force $= 400\,\mathrm{N}$, Distance $= 2\,\mathrm{m}$ \\
    \textbf{Required:} Work \\
    \textbf{Analysis:}
    \[
        W = F \times d
    \]
    \textbf{Solution:}
    \[
        W = 400\,\mathrm{N} \times 2\,\mathrm{m} = 800\,\mathrm{J}
    \]
    \textbf{Statement:} The work done is $800\,\mathrm{J}$.

    \item \textbf{Given:} Work $= 150\,\mathrm{J}$, Distance $= 2\,\mathrm{m}$ \\
    \textbf{Required:} Force \\
    \textbf{Analysis:}
    \[
        F = \frac{W}{d}
    \]
    \textbf{Solution:}
    \[
        F = \frac{150\,\mathrm{J}}{2\,\mathrm{m}} = 75\,\mathrm{N}
    \]
    \textbf{Statement:} The force exerted is $75\,\mathrm{N}$.

    \item \textbf{Given:} Force $= 20\,\mathrm{N}$, Work $= 400\,\mathrm{J}$ \\
    \textbf{Required:} Distance \\
    \textbf{Analysis:}
    \[
        d = \frac{W}{F}
    \]
    \textbf{Solution:}
    \[
        d = \frac{400\,\mathrm{J}}{20\,\mathrm{N}} = 20\,\mathrm{m}
    \]
    \textbf{Statement:} The rock was moved $20\,\mathrm{m}$.

    \item \textbf{Given:} Force $= 400\,\mathrm{N}$, Distance $= 0\,\mathrm{m}$ \\
    \textbf{Required:} Work \\
    \textbf{Analysis:}
    \[
        W = F \times d
    \]
    \textbf{Solution:}
    \[
        W = 400\,\mathrm{N} \times 0\,\mathrm{m} = 0\,\mathrm{J}
    \]
    \textbf{Statement:} The work done is $0\,\mathrm{J}$.
\end{enumerate}



\end{document}